---
title: "Guide to Pitch Plots"
author: "Abhishek A. Mishra"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide to Pitch Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is the guide for using Pitch Plots in ggshakeR

These plots aim to plot events on a pitch hence the name...Pitch Plots! 

Currently, ggshakeR houses 5 Pitch Plots:

* plot_pass()
* plot_heatmap()
* plot_sonar()
* plot_passflow()
* plot_shot()

Let's learn simple guides on how to use them!

# plot_shot()
Characteristics:

* Only works with Understat data
* Has three types: hexbin, density, or point (default)

The easiest Pitch Plot function to use! To use this package, which *only works with Understat data*, we need the [understatr package](https://github.com/ewenme/understatr).

Once you have installed the package, put the package in your work session by writing:

```{r}
library(understatr)
```

We will use the understatr package to get the data for plot_shot(). Browse through the understatr package to get their data. As a sanity check, make sure the dataframe has columns with these names:

* X (not x)
* Y (not y)
* xG
* result
* name

Here, I am going to get Mohammed Salah's data. To learn more about how to get data, read [Nandy's excellent guide](https://sagnikdas1.medium.com/tabguide-1-making-shot-maps-1c030f08393e).

```{r, eval=FALSE}
shot_data = get_player_shots(player_id = 1250)
```

After that, simply write and execute the following code to get a beautiful shotmap:

```{r, eval=FALSE}
plot = plot_shot(shot_data,type = "density")
plot
```
![plot_shot() of Mohammed Salah](images/plot_shot().png){width=80%}

Note that, you can write hexbin, density, and point to get three different types of shotmaps. Try it out!

# plot_sonar(), plot_heatmap(), plot_passflow()
These three functions are quite similar in what they require.

* plot_sonar() gives you a pass sonar
* plot_heatmap() gives you a heatmap on the pitch
* plot_passflow() gives you a passflow map on the pitch

Here are some key things to know:

* plot_sonar() and plot_passflow() expect passing data
* All three functions require the data to have at minimum four columns named: __x, y, finalX, finalY__
* All three functions work on either Opta or Statsbomb data
* All three functions need a minimum of 4 columns named:
  + x (indicates starting x location)
  + y (indicates starting y location)
  + finalX (indicates ending x location for passes)
  + finalY (indicates ending y location for passes)
  
Let's first get some data! You can either import you data or use [Statsbomb's open free dataset](https://github.com/statsbomb/open-data)

In this example, I'll be using Statsbomb's Messi Data for LaLiga 2014/15:

```{r, eval=FALSE}
Comp <- FreeCompetitions() %>%
  filter(competition_id==11 & season_name=="2014/2015")
Matches <- FreeMatches(Comp)
StatsBombData <- StatsBombFreeEvents(MatchesDF = Matches, Parallel = T)
StatsBombData = allclean(StatsBombData)

plottingData = StatsBombData
```

Before plotting, I am going to rename my columns:

```{r, eval=FALSE}
plottingData = plottingData %>%
  rename("x"="location.x") %>%
  rename("y"="location.y") %>%
  rename("finalX"="pass.end_location.x") %>%
  rename("finalY"="pass.end_location.y")
```

Sweet, let's plot!

## plot_heatmap()

For the heatmap, we simply select our columns and plot! Note that we don't specify __dataType__ since default is set to Statsbomb, so we can simply write this:
```{r, eval=FALSE}
heatData = plottingData %>%
  select(c(x,y,finalX,finalY))
heatplot = plot_heatmap(heatData, type="bin")
heatplot
```
![plot_heatmap() of all of LaLiga's events in 2014/15](images/plot_heatmap().png){width=80%}

## plot_sonar()

For the pass sonar, we're going to a bit more data cleaning. I don't want everybody's passing sonar - that's redundant! 

For our purposes, I want Jordi Alba's passing sonar! First, let me get all passes from Jordi Alba:

```{r, eval=FALSE}
plottingData = plottingData %>%
  filter(type.name == "Pass") %>%
  filter(team.name == "Barcelona") %>%
  filter(player.name == "Jordi Alba Ramos")
```

Now I can construct a pass sonar! Default dataType is set to Statsbomb, so here we can simply write:
```{r, eval=FALSE}
sonarPlot = plot_sonar(plottingData)
sonarPlot
```
![plot_sonar() of all of Jordi Alba's passes from 2014/15](images/plot_sonar().png){width=80%}

## plot_passflow()

Since we already have Jordi Alba's passes, we can just construct the passflow like this:

```{r, eval=FALSE}
passflowPlot = plot_passflow(passflowPlot)
passflowPlot
```
![plot_sonar() of all of Jordi Alba's passes from 2014/15](images/plot_passflow().png){width=80%}

